\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-07 paper/paper.tex
Beautification
Added architecture section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}

@@

%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------

@@

\section{Related Work}
% Redstone was inspired by work done by the TigerBeetle team,
% and their work in testing the TigerBeetle database.
% However, the limitation of their work is that their simulator is compiled specifically for their software.

@@

\section{System Call Interception}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12.5pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newcommand{\vrsdust}[1]{\includegraphics[height=#1]{redstone_dust.png}}
% \newcommand{\vrswire}[1]{\includegraphics[height=#1]{redstone_wire.png}}

\newcommand{\txtrsdust}{\vrsdust{0.55cm} \hspace{0.1in}}
% \newcommand{\txtrswire}{\vrswire{0.6cm}

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}

@@

%-------------------------------------------------------------------------------
\section{\txtrsdust Introduction}
%-------------------------------------------------------------------------------

@@

\section{\txtrsdust Related Work}
% Redstone was inspired by work done by the TigerBeetle team,
% and their work in testing the TigerBeetle database.
% However, the limitation of their work is that their simulator is compiled specifically for their software.

@@

\section{\txtrsdust Architecture}

\begin{figure}
\includegraphics[width=0.45\textwidth]{redstone_architecture.jpeg}
\caption{General architecture of the Redstone framework}
\end{figure}

{\fontsize{12}{15}\selectfont 
Figure 1 provides a visual representation of the architecture powering Redstone.
The region marked "simulator space" represents the simulator process,
for which system calls are re-routed to the syscall implementations specified for the simulator run.
Within the simulator process there are multiple “machines”,
representations of physical machines that, in production, would actually be different machines.
Each of these machine abstractions have their own simulated disk space.
Each machine abstraction is associated with a child process,
called a “replica”,
of the simulator process that runs the actual functionality expected of the individual machine,
working with the machine’s “files” (the in-memory storage mocked up by the simulator).

\section{\txtrsdust System Call Interception}
